---
title: 'Model Results: Basic'
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
    vertical_layout: scroll
    social: menu
    navbar:
      - { title: "Janez Žibert, UL ZF in FRI, 2022", href: "https://apps.lusy.fri.uni-lj.si", target: _blank, align: right }


---

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(knitr)
library(dplyr)
library(tidyr)


library(ggplot2)
library(scales)

library(plotly)
library(stringr)

library(flexdashboard)
library(kableExtra)

rm(list=ls())




############################################
##### model data  ####
############################################

tdat = read.csv("epimod_latest.csv")



##### aux var. ########

# Here we define spaces as the big separator
point <- format_format(big.mark = " ", decimal.mark = ",", scientific = FALSE)

last_date = Sys.Date()


## colors
cases.col  = "#338D73"
hosp.col   = "cornflowerblue"
icu.col    = "red"
deaths.col = "grey"
  

```










Forecasts {data-icon="fa-signal"}
=======================================================================
  

Row {data-height=30}
-------------------------------------
  
Report made on: `r format(Sys.time(), "%d-%m-%Y %H:%M:%S")`.  




Row
-----------------------------------------------------------------------
  
### Short description
  
Forecasts are made for daily cases, hospital and intensive care units stays and daily deaths. Forecasts are made with the model [SEIRC19SI.v5](https://apps.lusy.fri.uni-lj.si). 


Row
-----------------------------------------------------------------------
  
### Projection: daily cases: 7-day smoothed average 
  
  
```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 25000

pg = ggplot(tdat, aes(x=day, y = OKU)) +
  
  geom_line(aes(color="7-days average: cases"), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("7-days average: cases" = cases.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot



```


Row
-----------------------------------------------------------------------
  
### Projection: actual hospitalizations 
  
  
```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}

maxy = 2000 

pg = ggplot(tdat, aes(x=day, y = HOS)) +
  
  geom_line(aes(color="actual hosp."), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("actual hosp." = hosp.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot



```




Row
-----------------------------------------------------------------------

### Projection: intensive care units
  
  
```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}


maxy = 400

pg = ggplot(tdat, aes(x=day, y = ICU)) +
  
  geom_line(aes(color="actual ICU"), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("actual ICU" =  icu.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot


```

Row
----------------------------------------------------------------------

### Projection deaths: 7-day average
  
  
```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}


maxy = 60

pg = ggplot(tdat, aes(x=day, y = DSM)) +
  
  geom_line(aes(color="7-days average: deaths"), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("7-days average: deaths" = deaths.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot



```

Projections: cumulative  {data-icon="fa-chart-bar"}
=======================================================================
  
```{r , echo=FALSE, warning=FALSE}

kdat = data.frame(day = tdat$day, 
                  CHOS = round(cumsum(tdat$HOSin),0),
                  CICU = round(cumsum(tdat$ICUin),0),
                  CDTH = round(cumsum(tdat$DSM),0)
                  )


```

Row
-----------------------------------------------------------------------
  
  
  
### Projection: cumulative hospital admissions


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 40000

pg = ggplot(kdat, aes(x=day, y = CHOS)) +
  
  geom_line(aes(color="cum. hosp. adm."), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("cum. hosp. adm." = hosp.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot




```


Row
-----------------------------------------------------------------------
  
  
### Projection: cumulative ICU admissions


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 7000

pg = ggplot(kdat, aes(x=day, y = CICU)) +
  
  geom_line(aes(color="cum. ICU adm."), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("cum. ICU adm." = icu.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot




```


Row
-----------------------------------------------------------------------
  
  
  
### Projection: cumulative deaths


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 7000

pg = ggplot(kdat, aes(x=day, y = CDTH)) +
  
  geom_line(aes(color="cum. deaths"), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("cum. deaths" = deaths.col)) +
  
  ylab("number") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot




```






Weekly Incidence {data-icon="fa-chart-bar"}
=======================================================================


```{r , echo=FALSE, warning=FALSE}

widat = data.frame()

for (w in seq(7, max(tdat$day)-40, 7) )
{
  week_num = round(w/7,0)
  
  w.inc.cases = round(7*(tdat$OKU[tdat$day==w]), digits = 0)
  
  w.inc.hosp = round( sum( tdat$HOSin[tdat$day>(w-7) & tdat$day<=w]), digits = 0)
  
  w.inc.icu = round( sum( tdat$ICUin[tdat$day>(w-7) & tdat$day<=w]), digits = 0)
  
  w.inc.deaths = round(7*(tdat$DSM[tdat$day==w]), digits = 0)
  
  
  hdat = data.frame(week =  week_num,
                    w.inc.cases = w.inc.cases,
                    w.inc.hosp  = w.inc.hosp,
                    w.inc.icu  = w.inc.icu,
                    w.inc.deaths = w.inc.deaths)
  
  widat = rbind(widat, hdat)
  
}




```





Row
-----------------------------------------------------------------------
  
### Weekly incidence: cases


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}


maxy = 1.1*max(widat$w.inc.cases)

pg1 = ggplot(widat, aes(x=week, y = w.inc.cases)) +
  
  geom_col( stat="identity", position=position_dodge(), color = cases.col, fill= cases.col, alpha = 0.7, width=0.5) +
  
  scale_x_continuous(breaks = seq(0,max(widat$week), 5)) +
  scale_y_continuous(labels = point) +
  coord_cartesian(ylim = c(0, maxy))+

  ylab("number") + xlab("week") + 
  

  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12))



myplot = ggplotly(pg1, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot

```




Row
-----------------------------------------------------------------------
  
### Weekly incidence: hospital admissions 


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 1.3*max(widat$w.inc.hosp)

pg1 = ggplot(widat, aes(x=week, y = w.inc.hosp)) +
  
  geom_col( stat="identity", position=position_dodge(), color = hosp.col, fill= hosp.col, alpha = 0.7, width=0.5) +
  
  scale_x_continuous(breaks = seq(0,max(widat$week), 5)) +
  scale_y_continuous(labels = point) +
  coord_cartesian(ylim = c(0, maxy))+

  ylab("number") + xlab("week") + 
  

  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12))



myplot = ggplotly(pg1, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot

```


Row
-----------------------------------------------------------------------
  
### Weekly incidence: ICU admissions 


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}



maxy = 1.3*max(widat$w.inc.icu)

pg1 = ggplot(widat, aes(x=week, y = w.inc.icu)) +
  
  geom_col( stat="identity", position=position_dodge(), color = icu.col, fill= icu.col, alpha = 0.7, width=0.5) +
  
  scale_x_continuous(breaks = seq(0,max(widat$week), 5)) +
  scale_y_continuous(labels = point) +
  coord_cartesian(ylim = c(0, maxy))+

  ylab("number") + xlab("week") + 
  

  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12))



myplot = ggplotly(pg1, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot

```


Row
-----------------------------------------------------------------------
  
### Weekly incidence: deaths


```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=7}


maxy = 1.3*max(widat$w.inc.deaths)

pg1 = ggplot(widat, aes(x=week, y = w.inc.deaths)) +
  
  geom_col( stat="identity", position=position_dodge(), color = deaths.col, fill= deaths.col, alpha = 0.7, width=0.5) +
  
  scale_x_continuous(breaks = seq(0,max(widat$week), 5)) +
  scale_y_continuous(labels = point) +
  coord_cartesian(ylim = c(0, maxy))+

  ylab("number") + xlab("week") + 
  

  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12))



myplot = ggplotly(pg1, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot

```


Vaccination  {data-icon="fa-vial"}
=======================================================================
  



Row
-----------------------------------------------------------------------
  
### Vaccination rates
  
```{r , echo=FALSE, warning=FALSE, fig.width=14, fig.height=12}


maxy = 100

pg = ggplot(tdat, aes(x=day, y = VACC.rate*100)) +
  
  geom_line(aes(color="vaccination rate"), size=1.7 ) +
  
  scale_y_continuous(labels = point) +
  scale_x_continuous(breaks = seq(0,max(tdat$day), 28)) +
  
  coord_cartesian(ylim = c(0, maxy), xlim = c(0, max(tdat$day) - 70)) +
  
  scale_color_manual(values = c("vaccination rate" = "orange")) +
  
  ylab("percentages") +
  
  theme_bw() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 30)) +
  theme(text = element_text(size=12)) 


myplot = ggplotly(pg, height = 600) %>%
  config(displayModeBar = F) %>%
  layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, yanchor = "top", y = -0.2, title = list(text = "<b></b>"))) %>%
  layout(paper_bgcolor='transparent') %>%
  layout(yaxis = list(hoverformat = '.1f')) 


# correct label names in plotly
for (i in 1:length(myplot$x$data)){
  if (!is.null(myplot$x$data[[i]]$name)){
    myplot$x$data[[i]]$name =  gsub("\\(","",str_split(myplot$x$data[[i]]$name,",")[[1]][1])
  }
}

myplot




```

